---
title: "Learning Hub Accounts Clean Up"
format: html
---

This script looks into the list of people that have participated in NCEAS Learning Hub course and identify which accounts can be deleted. To do this we look into 3 data sets:
-   **participants_list:** List of all participants in a certain period of time. This information comes from collecting participants from every course run during the review period.
-   **workbench_active_accounts:** list accounts that are not locked in Posit Workbench. This data comes directly form the Posit Workbench administrator account (Ask Thomas).
-   **ldap:** list of LDAP accounts


## Set up

```{r}
library(tidyverse)
library(googlesheets4)
```


## Read in data
The url in this step needs to be updated every time we are doing the clean up process.
The `read_sheet()` function reads directly from the file's url. Copy and paste the url for each for the data sets need.


```{r}

## current year: 2023-2024

participants_list <- read_sheet("https://docs.google.com/spreadsheets/d/1rXo78GuF7cC8vRaxi4kV7Hxc7eDQAk52c9ZTxKXG8RU/edit?gid=0#gid=0", sheet = "participants_list") %>% 
    filter(!is.na(name))

workbench_accounts <- read_sheet("https://docs.google.com/spreadsheets/d/1rXo78GuF7cC8vRaxi4kV7Hxc7eDQAk52c9ZTxKXG8RU/edit?gid=0#gid=0", sheet = "Active")


ldap <- read_sheet("https://docs.google.com/spreadsheets/d/1rXo78GuF7cC8vRaxi4kV7Hxc7eDQAk52c9ZTxKXG8RU/edit?gid=0#gid=0", sheet = "LDAP")

```


## List of participants that accounts can be deleted

```{r}
participants_delete <- participants_list %>% 
    filter(delete == TRUE)
```

Creating a list of the accounts that will not be deleted to consider in the next round of clean-up. The reason that we are not deleting this accounts is because this users are in a ongoing course at the time being.
```{r}

participants_keep <- participants_list %>% 
    filter(delete == FALSE)

```


## List of accounts that can be bloked in Posit Workbench

```{r}
workbench_block <- participants_delete %>% 
    left_join(workbench_accounts, by= "username") %>% 
    filter(is.na(resident)) %>% 
    select(name, last_name, username)
```


## LDAP accounts to be deleted



